#Data Analysis

## Importing Data

```{r Import, message=FALSE}
library(readxl)
DatasetForRProject <- read_excel("DatasetForRProject.xlsx")
View(DatasetForRProject)
```

## Descriptive Statistics

```{r DescriptiveStat, message=FALSE}
summary(DatasetForRProject)
```

The General Average Wage has much higher measures of spread than median measures of spread.
This may indicate that there are large outliers influencing the average wage to be higher.
If we look at wages-by-degree, it seems like having a degree is much more helpful for wages than
not having a degree.

```{r LineGraphs, message=FALSE}
library(ggplot2)
ggplot(data=DatasetForRProject, aes(x=Year, y=GeneralMedianWage, group=1)) +
  geom_line()+
  geom_point()
ggplot(data=DatasetForRProject, aes(x=Year, y=GeneralAverageWage, group=1)) +
  geom_line()+
  geom_point()
```

This seems like average has less point-to-point variation than the median wage category. 

```{r InitialCorr}
library(GGally)
ggscatmat(DatasetForRProject, columns = 1:9,
          alpha=0.1)
```

It seems like year, CPI, and average and median wages are all correlated. The ones not correlated are non-degree earners. In order to analysis on this, we will have to treat this as a time series.

